% -----------------------------
% HOW TO USE THIS TEMPLATE
% 1. Paste this into Overleaf as main.tex
% 2. Edit the variables under "EDIT THESE" for name, links, email, phone
% 3. Turn sections on or off by setting includeProjects, includeSRS, includeRA to true or false
% 4. Add entries by copying an existing block, then changing the text
% 5. If you get "Runaway argument", it almost always means you accidentally commented out a closing brace with %
% -----------------------------

\documentclass[letterpaper,11pt]{article}

% Fixes the "Font shape ... bx/sc undefined" warning for bold small caps
\usepackage{lmodern}

\usepackage[left=0.5in,right=0.5in,top=0.7in,bottom=0.65in]{geometry}

\usepackage{ifthen}
\newboolean{includeProjects}
\newboolean{includeSRS}
\newboolean{includeRA}
\setboolean{includeProjects}{true}
\setboolean{includeSRS}{true}
\setboolean{includeRA}{true}

\usepackage{latexsym}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.35in}
\addtolength{\evensidemargin}{-0.4in}
\addtolength{\textwidth}{0.8in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% -----------------------------
% Helper commands
% -----------------------------

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}

% Usage:
% \resumeSubheading{Title}{Dates}{Org or team}{Location}
%   \resumeItemListStart
%     \resumeItem{Bullet}
%   \resumeItemListEnd
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

% Usage:
% \resumeProjectHeading{\textbf{Name} $|$ \emph{Tech}}{}
\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}

% Publications list. This fixes wrapping and keeps year aligned right.
\newcommand{\resumePubListStart}{\begin{itemize}[leftmargin=0in, label={}, itemsep=4pt, topsep=0pt, parsep=0pt, partopsep=0pt]}
\newcommand{\resumePubListEnd}{\end{itemize}}
% Usage:
% \resumePub{Title}{(venue, authors, note).}{Year}
\newcommand{\resumePub}[3]{%
  \item
  \begin{tabularx}{0.97\textwidth}{@{}X r@{}}
    \textbf{#1} #2 & #3 \\
  \end{tabularx}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% -----------------------------
% EDIT THESE
% -----------------------------
\newcommand{\FullName}{John Doe}
\newcommand{\PortfolioText}{portfolio: johndoe.dev}
\newcommand{\PortfolioUrl}{https://johndoe.dev}
\newcommand{\Phone}{+1 (555) 123-4567}
\newcommand{\Email}{john.doe@gmail.com}
\newcommand{\LinkedInText}{linkedin.com/in/johndoe}
\newcommand{\LinkedInUrl}{https://www.linkedin.com/in/johndoe/}
\newcommand{\GitHubText}{github.com/johndoe}
\newcommand{\GitHubUrl}{https://github.com/johndoe}

\begin{document}

% Header
% Note: If you see a "Runaway argument" error, check you did not put a % inside any {...} argument.
\begin{center}
  \textbf{\huge \scshape \FullName} \\[3pt]
  \href{\PortfolioUrl}{\textbf{\PortfolioText}} \\[3pt]
  \small \Phone $|$
  \small \Email $|$
  \href{\LinkedInUrl}{\LinkedInText} $|$
  \href{\GitHubUrl}{\GitHubText}
\end{center}

% -----------------------------
% EDUCATION
% -----------------------------
\section{Education}
\resumeSubHeadingListStart

  \item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{Massachusetts Institute of Technology (MIT)} & \\
    \textit{\small M.S. in Computer Science (AI and Systems)} & \small Jun 2027 \\
    \textit{\small B.S. in Electrical Engineering and Computer Science} & \small May 2025 \\
  \end{tabular*}\vspace{-5pt}

  \resumeSubheading
    {University of Oxford}{Sep 2024 -- Dec 2024}
    {Visiting Student, Computer Science}{Oxford, United Kingdom}
    \resumeItemListStart
      \resumeItem{Completed graduate coursework in probabilistic modeling, optimization, and distributed systems.}
      \resumeItem{Built a research prototype for privacy preserving on device inference using quantization and secure aggregation.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-9pt}

% -----------------------------
% EXPERIENCE
% -----------------------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {Software Engineering Intern}{May 2026 -- Aug 2026}
  {\href{https://www.google.com}{Google Ads Infrastructure, Full time}}{Mountain View, CA}
  \resumeItemListStart
    \resumeItem{Reduced p95 request latency by 18 percent by redesigning a fanout path and adding cache aware batching in Go.}
    \resumeItem{Built a streaming backfill pipeline in Apache Beam to migrate 2.3B records with exactly once semantics.}
    \resumeItem{Shipped end to end monitoring, alerts, and dashboards, lowering incident triage time from 25 minutes to 8 minutes.}
  \resumeItemListEnd

\resumeSubheading
  {Machine Learning Research Intern}{Jun 2025 -- Aug 2025}
  {\href{https://openai.com}{OpenAI, Full time}}{San Francisco, CA}
  \resumeItemListStart
    \resumeItem{Improved a retrieval augmented generation benchmark score by 9.4 points through reranking and query rewriting.}
    \resumeItem{Implemented scalable training utilities for multi GPU runs using PyTorch DDP, speeding experiments by 2.1x.}
    \resumeItem{Co authored an internal report with ablations, safety checks, and reproducibility scripts for model evaluation.}
  \resumeItemListEnd

\ifthenelse{\boolean{includeRA}}{
\resumeSubheading
  {Research Assistant}{Sep 2024 -- Present}
  {\href{https://www.csail.mit.edu}{MIT CSAIL, Human Centered AI Group}}{Cambridge, MA}
  \resumeItemListStart
    \resumeItem{Reproduced baselines for multimodal agent evaluation and built a simulation harness for controlled experiments.}
    \resumeItem{Designed a user study protocol and analysis pipeline, including power analysis, preregistration, and reporting.}
    \resumeItem{Maintained an open source codebase with CI, tests, and documentation, enabling external contributors.}
  \resumeItemListEnd
}{}

\resumeSubHeadingListEnd
\vspace{-10pt}

% -----------------------------
% SELECTED RESEARCH / PUBLICATIONS / SPEAKING
% -----------------------------
\ifthenelse{\boolean{includeSRS}}{
\section{Selected Research, Publications, and Speaking}
\resumePubListStart
  \resumePub
    {Neural Scheduling for Large Scale Systems}
    {(with A. Smith, B. Lee). Preprint.}
    {2026}
  \resumePub
    {Robust Retrieval Pipelines for Production RAG}
    {(Poster). NeurIPS Workshop on Efficient Systems.}
    {2025}
  \resumePub
    {Talk, Practical MLOps for Multimodal Evaluation}
    {(Invited). MIT AI Seminar Series.}
    {2025}
  \resumePub
    {Patent, Adaptive Batching for Low Latency Fanout Services}
    {(Provisional).}
    {2026}
\resumePubListEnd
\vspace{-8pt}
}{}

% -----------------------------
% PROJECTS
% -----------------------------
\ifthenelse{\boolean{includeProjects}}{
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
  {\href{https://github.com/johndoe/atlas-rag}{\textbf{AtlasRAG}} $|$ \emph{Python, FastAPI, PyTorch, FAISS, Docker}}{}
\resumeItemListStart
  \resumeItem{Built a local first RAG system with document chunking, vector search, reranking, and evaluation harnesses.}
  \resumeItem{Added reproducible benchmarks with synthetic and real datasets, tracking accuracy, latency, and cost per query.}
\resumeItemListEnd

\resumeProjectHeading
  {\href{https://github.com/johndoe/telemetry-kit}{\textbf{TelemetryKit}} $|$ \emph{Go, OpenTelemetry, Prometheus, Grafana}}{}
\resumeItemListStart
  \resumeItem{Created a plug and play observability toolkit for microservices with tracing, metrics, and alert templates.}
  \resumeItem{Demonstrated a 3x faster incident root cause workflow using standardized dashboards and correlation IDs.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-10pt}
}{}

% -----------------------------
% AWARDS
% -----------------------------
\section{Awards and Achievements}
\resumeSubHeadingListStart

  \resumeSubheading
    {Google Student Researcher Grant}{2026}
    {\small Awarded funding for work on evaluation methodologies for deployed language model systems.}{}

  \resumeSubheading
    {Open Source Fellowship, Linux Foundation}{2024}
    {\small Contributed features and tests to a high traffic networking library used in production systems.}{}

\resumeSubHeadingListEnd
\vspace{-10pt}

% -----------------------------
% SKILLS
% -----------------------------
\section{Technical Skills}
\begin{itemize}[leftmargin=0in, label={}]
  \small{\item{
    \textbf{Languages}: Python, C++, Go, Rust, TypeScript, SQL \\[1pt]
    \textbf{ML and AI}: PyTorch, JAX, Transformers, FAISS, Ray, Weights and Biases \\[1pt]
    \textbf{Backend}: FastAPI, gRPC, Kafka, Redis, Postgres, Docker, Kubernetes \\[1pt]
    \textbf{Systems}: Linux, OpenTelemetry, Prometheus, Grafana, CI and CD, Terraform \\[1pt]
    \textbf{Tools}: Git, Bash, VS Code, Jupyter, Figma, Unity, ROS2
  }}
\end{itemize}

\end{document}
